% ======================================================================================================
% NOTES, TODOS
% ======================================================================================================

\subsection{Data Extraction Form}
Kitchenham and Charter \cite{kitchenham_guidelines_2007} state that a well-designed data extraction form is helpful to gather information from primary studies to address research questions. To ensure this in our study, we utilised the web-based tool, \textit{parsif.al}, to structure and design the data extraction form used to collect data from the selected articles. The data extraction form used in this systematic literature review is presented in Table \ref{tbl:extraction}.

% Note that, the data extraction form is, and also was in our case, continuously evolving during the full-text review process. 


\begin{table}[h]
\small
\centering
\caption{ Data Extraction Form}
\label{tbl:extraction}
\begin{NiceTabular}{p{4cm}p{8cm}}
\toprule
    \textbf{Data Point} & \textbf{Options/Explanation} \\
    \midrule
    \textbf{Aim of research} & Summarized version of the aim of the paper \\ 
    \textbf{Targeted sector} & The studied or targeted Industry 4.0 sector \\
    \textbf{DT purpose} & The function or purpose the proposed Digital Twin \\ 
    \textbf{Enabling technology} & Technology integrated with Digital Twin to provide security service \\ 
    \textbf{Security mechanism} &  The Security Mechanism Employed To Secure Communication Channel   \\ 
    \textbf{Contribution category} & Framework, Algorithms, Architecture, Model, Platform \\
    \textbf{Study type} & Paper With Case-study, Experiment Based, Theoretical Concept, Review Paper Science  \\
\bottomrule
\end{NiceTabular}
\end{table}

The contribution categories and study types provide a useful framework for identifying patterns and trends in the research literature. For example, if we have more papers that focus on theoretical concepts than experimental study types, we can conclude that the research community is still in the early stages of understanding the problem and that there is a need for more empirical research. 

The Contribution categories differ in terms of the type of contribution that they make to the research. For example, a framework provides a set of guidelines or principles, while an algorithm provides a step-by-step procedure for solving a problem. The Study types differ in terms of the methodology that is used to conduct the research. For example, a case study is an in-depth investigation of a particular sector, while a paper's study type is classified as an "Experiment Based" if it reports the results of an experiment that was conducted to test a hypothesis. A paper's study type is classified as a "Review Paper" if it summarizes and  evaluates the existing literature.
