% ======================================================================================================
% NOTES, TODOS
% ======================================================================================================
% describe how to perform the detail assessment
% use numeral scale 
% Are the aim of the article clearly stated?
% Is the implementation detail explained adequately 
% does the study has direct link to research question 1 and/or question 2. 
% 
\subsection{Quality Assessment Checklist}
After papers are selected using the inclusion and exclusion criteria, we also evaluate the papers and give scores using a quality assessment checklist. The evaluation  is performed during the phase of conducting the review. The goal of this process is to identify and eliminate articles that don't meet the minimum threshold quality. 

The quality assessment checklist that defines the detailed assessment criteria  is outlined below.
% Besides the inclusion and exclusion criteria, it is important to evaluate the quality of the research study\cite{kitchenham_guidelines_2007}.
\begin{itemize}
    \item \textbf{QA1:} Abstract: Is the research question(aim) clearly defined and relevant to the field of study?
    \item \textbf{QA2:} Abstract: Does the study propose any new security solutions or improvements to existing ones? ensuring the security (I)IoT application using Digital Twin?
    \item \textbf{QA3:} Methodology: Does the study adequately explain a methodology or framework to secure (I)IoT applications using DT?
    \item \textbf{QA4:} Methodology: Does the study conducted an experiment(test-bed) or use case to validate the hypothesis?
    \item \textbf{QA5:}Methodology: Does the study provide detailed procedures to ensure secure communication between DT and IoT?
    \item \textbf{QA5:}Result: Are the results of the study clearly presented and supported by the data?
    \item \textbf{QA5:}Discussion: Does the research provide a discussion and analysis of the implications and potential future work in the field?
\end{itemize}
% The quality assessment questions outlined above were evaluated using a numerical metric scoring system, with a range of 1-5, where 1 represents an irrelevant article and 5 represents a highly relevant and qualified article. The level of agreement in answering the quality checklist questions was determined through a categorical classification system, comprising of "Agree," "Somewhat Agree," "Neutral," "Somewhat Disagree," and "Disagree." These categories were assigned corresponding weight values, with "Agree" being assigned the highest weight value of 5 and "Disagree" being assigned the lowest weight value of 1. This scoring system helped to ensure that we evaluated research studies in a fair and consistent way so that the studies that were the most relevant and of the highest quality were selected for the review.

% The number of articles and their scores is depicted in the diagram [blab bla]. 
